\thetitle

### 2013-04-18 tfpie/tfpie.tex
Some writing on world.

Although the combination of data and functionality may seem simple,
objects enable new forms of abstraction and composition. That is,
objects open up new approaches to the construction of computations. By
studying these new approaches, we can distill new design
principles. Because we understand objects are just the combination of
data and functionality, we can understand how all of these principles
apply in the familiar context of programming with functions. In short,
the better you are at programming with objects, the better you will be
at programming with functions, and \emph{vice versa}.

\end{enumerate}

@@

>>>>

Although the combination of data and functionality may seem simple,
objects enable new forms of abstraction and composition. That is,
objects open up new approaches to the construction of computations. By
studying these new approaches, we can distill new design
principles. Because we understand objects are just the combination of
data and functionality, we can understand how all of these principles
apply in the familiar context of programming with functions. 
\end{enumerate}

@@

Programming in the first semester is often oriented around interactive
event-driven video games.  The basic design of a video game involves
defining a data representation for states of the game and functions
for transitioning between states based on events such as clock ticks,
keyboard input, or mouse events.  The design of a game thus involves
the design of data and functions on that data; in other words, the
game involves the design of objects.  We therefore continue in the
second semester with the use of programming video games but supplement
the course with a library for doing so in an object-oriented style.
Figure~\ref{fig:world} gives an example written in both the functional
style and object-oriented style.
